A Switching Planner for Combined Task and Observation Planning

### 2010-11-24 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
tiny change.
I need to make some big changes now. I need to deal with the turnery nature of sequential assumptions. And then I have to make the distinction between a plan and a trace clear. Heaps of work.

Because $\state_0$ is abstract, and because actions can have
preconditions that are not uniformly true in the underlying
(resp. abstract) belief-state, we must make two further adjustments to
the problem posed to the sequential planner. First, if
$\action\in\actions$ has a precondition that is not true with
probability $1$ in $\bstate_0$, then before it is executed blindly,
the sequential continual planning switches to a decision-theoretic
session, discussed in detail below. Overall, by scheduling $\action$
the sequential planner makes a naive assumption about the possibility
of the agent eventually ``committing'' to the truth values of specific
state propositions in $\poss(\action)$. The role of decision-theoretic
plans is to examine the validity of assumptions about the runtime
state of sequential planning. Second, if the truth value of $\prop$ is
not known, and no assumption is made about it in the current abstract
state, then if $\prop \in
\poss(\action)$ we have that action $\action$ is not applicable.

@@

For the management of switching, execution of either a
$\assumptiveDT{i}$ action, or $\actions.\poss(\action_i)$, returns
control to the sequential planner. At that point, if a dual is
executed, then the sequential planner must replan with $\bstate_0$
equal to the current belief. Otherwise, if $\actions.\poss(\action_i)$
is executed, then the current sequential plan is executed until
further sensing is scheduled, or to completion. In our project the
rewards, i.e., function $\$:2^\propositions\to\Re$, for the POMDP
posed to decision-theoretic planning are sourced from a motivational
component of our robotic architecture.

>>>>

Because $\state_0$ is abstract, and because actions can have
preconditions that are not uniformly true in the underlying
(resp. abstract) belief-state, we must make two further adjustments to
the problem posed to the sequential planner. First, if
$\action\in\actions$ has a precondition that is not true with
probability $1$ in $\bstate_0$, then before it is executed blindly,
the sequential continual planning switches to a decision-theoretic
session, discussed in detail below. Overall, by scheduling $\action$
the sequential planner makes a naive assumption about the possibility
of the agent eventually ``committing'' to the truth values of specific
state propositions in $\poss(\action)$. The role of decision-theoretic
plans is to examine the validity of assumptions about the runtime
state of sequential planning. Second, if in the current state \state\
the value of $\prop$ is $\#$ ---because a truth value is not specified
in $\state_0$ and no assumption is made about it in the plan
to \state--- then if $\prop \in \poss(\action)$, or if $\prop$ is the
subject of a positive or negative effect of $\action$, we have that
action $\action$ is not applicable in \state.

@@

For the management of switching, execution of either a dual action of
the form $\assumptiveDT{i}$, or the $\actions.\poss(\action_i)$,
returns control to the sequential planner. At that point, if a dual is
executed, then the sequential planner must replan with $\bstate_0$
equal to the current belief. Otherwise, if $\actions.\poss(\action_i)$
is executed, then the current sequential plan is executed until
further sensing is scheduled, or to completion. In our project the
rewards, i.e., function $\$:2^\propositions\to\Re$, for the POMDP
posed to decision-theoretic planning are sourced from a motivational
component of our robotic architecture.
